Language-Based Security for Low-Level MPC

### 2024-05-15 ppdp24/main.tex
checkpoint

\begin{abstract}
  Secure Multi-Party Computation (MPC) protocols is an important
  enabling technology for data privacy in modern distributed
  applications. Currently, proof methods for low-level MPC protocols
  are primarily manual and thus tedious and error-prone, and are also
  non-standardized and unfamiliar to most PL theorists. We develop a
  new staged programming language for defining a variety of low-level
  protocols with probabilistic features. We also formulate a
  collection of confidentiality and integrity hyperproperties for our
  language model that are familiar from information flow, including
  conditional noninterference, delimited release, and robust
  declassification. We demonstrate their relation to standard MPC
  threat models of passive and malicious security, and how they can be
  leveraged in security verification of protocols. To prove these
  properties we develop automated tactics in $\mathbb{F}_2$ that
  can be integrated with separation-logic style reason. 
\end{abstract}

>>>>

\begin{abstract}
  Secure Multi-Party Computation (MPC) protocols is an important
  enabling technology for data privacy in modern distributed
  applications. Currently, proof methods for low-level MPC protocols
  are primarily manual and thus tedious and error-prone, and are also
  non-standardized and unfamiliar to most PL theorists. As a step
  towards better language support and language-based enforcement, we
  develop a new staged PL for defining a variety of low-level
  probabilistic MPC protocols. We also formulate a collection of
  confidentiality and integrity hyperproperties for our language model
  that are familiar from information flow, including conditional
  noninterference, delimited release, and robust declassification. We
  demonstrate their relation to standard MPC threat models of passive
  and malicious security, and how they can be leveraged in security
  verification of protocols. To prove these properties we develop
  automated tactics in $\mathbb{F}_2$ that can be integrated with
  separation-logic style reasoning.
\end{abstract}
